EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-16 draft.tex
Two last questions

However, when we compare the two
options, we find some subtle differences: When using one or two
workers, using 5 populations takes less time in most cases. 
In Table~\ref{tab:time} results with p-value of the two-tailed Wilcoxon
signed-ranks test was grater than the level of significance of 0.05 
(i.e., accepting the null hypothesis of inequality) are marked in boldface.
A reason for this could be that the migration of individuals takes more time to
reach the worker. % how come? - JJ
For instance, when a single worker has 10 populations, only
after processing every one of them, it will start receiving mixed populations.  Although, in
all cases, and even with a single worker, populations are heterogeneous, this
advantage takes more time to propagate. % which advantage? - JJ
With four workers, almost the same
results can be achieved regardless of our selection between five or ten
populations. Also, there is not much difference between 4 and 8 workers, when
using five populations, which might indicate that some workers are
idling while populations are being processed by other workers. In
general, we can observe that keeping a ratio between the number of workers and populations a bit over 1:1  exploits better the computing
resources available. This also decreases the relation between the
overhead needed to migrate and process incoming and outgoing
population and the total computing time: more populations will need
more time to do that.

>>>>

However, when we compare the two
options, we find some subtle differences: When using one or two
workers, using 5 populations takes less time in most cases. 
In Table~\ref{tab:time} results with p-value of the two-tailed Wilcoxon
signed-ranks test was grater than the level of significance of 0.05 
(i.e., accepting the null hypothesis of inequality) are marked in boldface.
A reason for this could be that when having more populations, the migration
of individuals takes more time to reach to all of them.
% how come? - JJ  - Explained a bit more - M
For instance, when a single worker has 10 populations, only
after processing every one of them, it will start receiving mixed populations.  Although, in
all cases, and even with a single worker, populations are heterogeneous, but
mixed individuals take more time to propagate. % which advantage? - JJ - Individuals from other pops - M
With four workers, almost the same
results can be achieved regardless of our selection between five or ten
populations. Also, there is not much difference between 4 and 8 workers, when
using five populations, which might indicate that some workers are
idling while populations are being processed by other workers. In
general, we can observe that keeping a ratio between the number of workers and populations a bit over 1:1  exploits better the computing
resources available. This also decreases the relation between the
overhead needed to migrate and process incoming and outgoing
population and the total computing time: more populations will need
more time to do that.
